EasyMerge - A New Tool for Code Clones Refactoring

### 2014-03-18 paper/paper.tex
update paper

\subsection{Preprocessing}
The first step of EasyMerge is to run CloneDigger at target source tree, take its output and format and standardize it for our own usage.
The core of this step is to classify code clones and get the ones that we not only can but also want to merge.

@@

>>>>

\subsection{Preprocessing}
The first step of EasyMerge is to run CloneDigger at target source tree, take its output and format and standardize it for our own usage.
The core of this step is to classify code clones and get the ones that we not only can but also want to merge. Although CloneDigger takes
a dozen configuration parameters, we use most of them as defaults. For our preprocessing, we only override {\bf distance-threshold} and {\bf size-threshold}
to {\bf 10} and {\bf 4} for we are only interested in clone segments of no more than 10 anti-unification distance from each other and no less than 4 lines in length.

Additionally, we put identical clone pairs into sets. For example, if we have three pairs of [A, B], [B, C], [C, A] from CloneDigger's output, we generate a clone set
of [A, B, C] instead for our following merging stage. As not all clone sets can be handled by our algorithm, we also implement a filter to remove all unrefactorable
clones before entering next step.

\subsection{Recommendation Evaluation}
Although EasyMerge can handle multiple types of code clones, not all of them shall be recommended. As a matter of fact, we use a combination of 
package path analyzer and weighted evaluation formula to make our recommendation decisions.

@@

\section{Conclusion and Future Work}
Code clones are very common in medium to large scale software applications.
Detecting and refactoring unnecessary clones can help us provide cleaner, easier to understand, and readily reusable code.
However, there are many different types of clones and many subtle implications while dealing with them when coupling and
inheritance is involved. Our proposed solution, EasyMerge, is a clone refactoring tool based on anti-unification clone detector 
CloneDigger, that can handle most Type-1 clones and many Type-2 clones. It fixes external variable and function reference
and provide merge recommendation based on evaluation of externality and package information analysis.
